Thesis: draft

### 2021-04-17 draft.tex
plus minus finished stubborn people section in results

In this section we will discuss some results related to the network structure and network topologies of the different network models that are used in this thesis. We will mainly focus on the effect of a high clustering coefficient and a community structure. Two different opinion distributions are investigated
\begin{itemize}
	\item An initial $50/50$ opinion distribution: the initial fraction of nodes with opinion 0 is equal to $P_0(0) = 0.5$ and the initial fraction of nodes with opinion 1 is equal to $P_1(0) = 0.5$.
	\item An initial $20/80$ opinion distribution: the initial fraction of nodes with opinion 0 is equal to $P_0(0) = 0.2$ and the initial fraction of nodes with opinion 1 is equal to $P_1(0) = 0.8$. Hence, we are dealing with a minority and a majority opinion.
\end{itemize}
For both opinion distributions we investigate the evolution of the opinion fractions with time and the formation of echo chambers.\\
\newline
Before sharing the results, a quick disclaimer: Some of the results that are shared in this section, were already obtained by prof. Nicola Perra and prof. Luis E.C. Rocha in their paper \textit{"Modelling opinion dynamics in the age of algorithmic personalization"} (see reference \cite{Perra2019}). These results include the effect of a high clustering coefficient (Watts-Strogatz model) and a random network model. Similar results (albeit with a different network size and average degree) are included in this section to give a complete overview and to be able to compare a community structure to a high clustering coefficient.

@@

Figure \ref{ev_op_50_50} shows the results for the evolution of the fraction of opinion 0 over time, together with the standard deviation $\sigma$. Two different filtering algorithms are compared to each other, namely the PR method and the REC method (see Chapter \ref{chap3}, Section \ref{filter} for a detailed explanation). None of the network topologies, nor the filtering algorithms, is able to break the initial $50/50$ opinion distribution. Having a high clustering or a clear community structure has no impact on the prevalence of the opinions. The status quo is maintained and the system is not pushed towards a different equilibrium.

@@

  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ opinion distribution]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ distribution. Four different network models are used (each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS), $K = 10$, two slightly different values of the clustering coefficient are used ($\left<C\right> \sim 0.55$ and $\left<C\right> \sim 0.60$); \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. For each model two different filtering algorithms are compared to each other: the REC and the PR filtering algorithm. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?

@@

  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ opinion distribution]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ distribution. Four different network models are used (each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. For each model two different filtering algorithms are compared to each other: the REC and the PR filtering algorithm. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}

@@

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_frac_compl_stubb_REC_8x7.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_frac_compl_stubb_REC_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_frac_compl_stubb_REC_8x7.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_frac_compl_stubb_REC_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ opinion distribution, using the REC filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$)]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ distribution, using the REC filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$). Four different network models are used (each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\label{ev_op_50_50_stubb_REC}
\end{figure}

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_frac_compl_stubb_PR_8x7.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_frac_compl_stubb_PR_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_frac_compl_stubb_PR_8x7.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_frac_compl_stubb_PR_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ opinion distribution, using the PR filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$)]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ distribution, using the PR filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$). Four different network models are used (each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\label{ev_op_50_50_stubb_PR}
\end{figure}
\noindent
Figure \ref{ev_op_50_50_stubb_PR} shows the results for the evolution of the fraction of opinion 0 in the system for an initial $50/50$ opinion distribution and when using the PR filtering algorithm. Data points are again represented together with the standard deviation $\sigma$. Three different fractions of stubborn people (fracRes $=0$, fracRes $=0.4$ and fracRes $=0.8$) are compared to each other for the four different network models. The results don't differ from those obtained for the REC filtering algorithm. The status-quo is maintained, the initial $50/50$ opinion distribution does not change over time when introducing stubborn people and using the PR filtering algorithm.\\
\newline
Up till now, we have discussed the results for the formation of echo chambers and the evolution of the opinions when introducing a fraction of completely stubborn nodes in the system for an initial $50/50$ opinion distribution. Lets now look at the results for introducing a fraction of stubborn agents when we are dealing with an unbalanced initial opinion distribution, eg. an initial $20/80$ distribution.\\
\newline

@@

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_frac_compl_stubb_REC_20-80_8x7.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_frac_compl_stubb_REC_20-80_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_frac_compl_stubb_REC_20-80_8x7.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_frac_compl_stubb_REC_20-80_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ opinion distribution, using the REC filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$)]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ distribution, using the REC filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$). Four different network models are used (each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\label{ev_op_20_80_stubb_REC}
\end{figure}

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_frac_compl_stubb_PR_20-80_8x7.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_frac_compl_stubb_PR_20-80_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_frac_compl_stubb_PR_20-80_8x7.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_frac_compl_stubb_PR_20-80_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ opinion distribution, using the PR filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$)]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ distribution, using the PR filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$). Four different network models are used (each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\label{ev_op_20_80_stubb_PR}
\end{figure}

>>>>

In this section we will discuss some results related to the network structure and network topologies of the different network models that are used in this thesis. We will mainly focus on the effect of a high clustering coefficient and a community structure. Two different opinion distributions are investigated
\begin{itemize}
	\item An initial $50/50$ opinion distribution: the initial fraction of nodes with opinion 0 is equal to $P_0(0) = 0.5$ and the initial fraction of nodes with opinion 1 is equal to $P_1(0) = 0.5$.
	\item An initial $20/80$ opinion distribution: the initial fraction of nodes with opinion 0 is equal to $P_0(0) = 0.2$ and the initial fraction of nodes with opinion 1 is equal to $P_1(0) = 0.8$. Hence, we are dealing with a minority and a majority opinion.
\end{itemize}
For both opinion distributions we investigate the evolution of the opinion fractions with time and the formation of echo chambers. Two filtering algorithms will be compared to each other, namely the REC and the PR filtering algorithm, in order to investigate the possible interplay between those filtering algorithms and the network structures.\\
\newline
Before sharing the results, a quick disclaimer: Some of the results that are shared in this section, were already obtained by prof. Nicola Perra and prof. Luis E.C. Rocha in their paper \textit{"Modelling opinion dynamics in the age of algorithmic personalization"} (see reference \cite{Perra2019}). These results include the effect of a high clustering coefficient (Watts-Strogatz model) and a random network model. Similar results (albeit with a different network size and average degree) are included in this section to give a complete overview and to be able to compare a community structure to a high clustering coefficient.

@@

Figure \ref{ev_op_50_50} shows the results for the evolution of the fraction of nodes with opinion 0, $P_0(t)$, over time, together with the standard deviation $\sigma$. Two different filtering algorithms are compared to each other, namely the PR method and the REC method (see Chapter \ref{chap3}, Section \ref{filter} for a detailed explanation). None of the network topologies, nor the filtering algorithms, is able to break the initial $50/50$ opinion distribution. Having a high clustering or a clear community structure has no impact on the prevalence of the opinions. The status quo is maintained and the system is not pushed towards a different equilibrium.

@@

  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ opinion distribution]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ distribution. Four different network models are used, each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$: \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS), $K = 10$, two slightly different values of the clustering coefficient are used ($\left<C\right> \sim 0.55$ and $\left<C\right> \sim 0.60$); \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. For each model two different filtering algorithms are compared to each other: the REC and the PR filtering algorithm. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?

@@

  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ opinion distribution]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ distribution. Four different network models are used, each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$: \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. For each model two different filtering algorithms are compared to each other: the REC and the PR filtering algorithm. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}

@@

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_frac_compl_stubb_REC_8x7.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_frac_compl_stubb_REC_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_frac_compl_stubb_REC_8x7.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_frac_compl_stubb_REC_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ opinion distribution, using the REC filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$)]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ distribution, using the REC filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$). Four different network models are used, each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$: \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\label{ev_op_50_50_stubb_REC}
\end{figure}

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_frac_compl_stubb_PR_8x7.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_frac_compl_stubb_PR_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_frac_compl_stubb_PR_8x7.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_frac_compl_stubb_PR_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ opinion distribution, using the PR filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$)]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ distribution, using the PR filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$). Four different network models are used, each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$: \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\label{ev_op_50_50_stubb_PR}
\end{figure}
\noindent
Figure \ref{ev_op_50_50_stubb_PR} shows the results for the evolution of the fraction of opinion 0 in the system for an initial $50/50$ opinion distribution and when using the PR filtering algorithm. Data points are again represented together with the standard deviation $\sigma$. Three different fractions of stubborn people (fracRes $=0$, fracRes $=0.4$ and fracRes $=0.8$) are compared to each other for the four different network models. The results don't differ from those obtained for the REC filtering algorithm. The status-quo is maintained, the initial $50/50$ opinion distribution does not change over time when introducing stubborn people and using the PR filtering algorithm.\\
\newline
Up till now, we have discussed the results for the formation of echo chambers and the evolution of the opinions when introducing a fraction of completely stubborn nodes in the system for an initial $50/50$ opinion distribution. Lets now look at the results for introducing a fraction of stubborn agents when we are dealing with an unbalanced initial opinion distribution, eg. an initial $20/80$ distribution.\\
\newline

@@

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_frac_compl_stubb_REC_20-80_8x7.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_frac_compl_stubb_REC_20-80_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_frac_compl_stubb_REC_20-80_8x7.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_frac_compl_stubb_REC_20-80_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ opinion distribution, using the REC filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$)]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ distribution, using the REC filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$). Four different network models are used, each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$: \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\label{ev_op_20_80_stubb_REC}
\end{figure}

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_frac_compl_stubb_PR_20-80_8x7.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_frac_compl_stubb_PR_20-80_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_frac_compl_stubb_PR_20-80_8x7.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_frac_compl_stubb_PR_20-80_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ opinion distribution, using the PR filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$)]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ distribution, using the PR filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$). Four different network models are used, each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$: \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\label{ev_op_20_80_stubb_PR}
\end{figure}
